ZCB Pricing

### 2018-07-05 ZCB Pricing .Rmd
Extra plot

R <- implicit(0.08,0.8,0.005,0.05,1:50,seq(0,0.1,0.01))

@@

G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))

>>>>

R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01))

#============================================================================================
# Doing some plots

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

@@

G <- CN(0.08,0.8,0.005,0.05, I=1:100, J = seq(-0.3,0.5,0.01))

#============================================================================================
# Doing some plots

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
}
plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```
